
---
title: "Python resample discharge"
output: html_notebook
---

Script 1

This script reads measured discharge from main outlets and microwatersheds and should be
run first when starting from scratch.


Load Libraries and set the working directory for Python

```{r}

library(tidyr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(hydroGOF) 
library(reticulate) #Allows to use python in R
use_python("C:/Users/Sergio/AppData/Local/Microsoft/WindowsApps") #Location of python 


```

Here we use Python to import and resample the 10 min data measured at the outlets

```{python}

import pandas as pd
import matplotlib.pyplot as plt
import os
import numpy as np
import datetime

# Read 10 min data from Gavilanes

os.chdir("C:/Veracruz/SWAT/github-rswat-ver/data")

# Read and resample the 10 min data from Gavilanes

q_gav = pd.read_csv("Gavilanes_Q10min.csv",skiprows=0)

q_gav.Date = pd.to_datetime(q_gav.Date)

q_gav.set_index(q_gav["Date"],inplace=True)

q_gav_dd = pd.Series.to_frame(q_gav['Q_m3_s'].resample('D').mean())

q_gav_dd.reset_index(level=0, inplace=True)

# Read and resample the 10 min data from Pixquiac

q_pix = pd.read_csv("Pixquiac_Q10min.csv",skiprows=0)

q_pix.Date = pd.to_datetime(q_pix.Date)

q_pix.set_index(q_pix["Date"],inplace=True)

q_pix_dd = pd.Series.to_frame(q_pix['Q_m3_s'].resample('D').mean())

q_pix_dd.reset_index(level=0, inplace=True)

print(q_pix_dd.head())

```

Import observed variables from Python to R

```{r}

#Import from Python the Q obs main outlets
q_obs_gav <- py$q_gav_dd%>%
  mutate(Date =  as.Date(Date))

q_obs_pix <- py$q_pix_dd%>%
  mutate(Date =  as.Date(Date))

# Import observed q and p from micro-watershed
obs_micros <- read.csv("C:/Veracruz/SWAT/github-rswat-ver/data/Micros.csv")

```

Estimate FDC of simulated and convert to categorical variables with Python 

```{python}

#Declare the FDC function

def FDC (q):
    
    """ This function computes the FDC q is the dataframe column with Q values"""
    
    data = np.asarray(q[q.notnull()])
    
    data = -np.sort(-data,)
    
    name = pd.DataFrame(list(data))
    
    name["p"] = (name.index + 1)/(len(name) + 1)

    name.columns = ["q", "p"]
    
    return name


fdc_sim_PF = FDC((r.q_sim_micros.FLOW_OUT_355))
fdc_sim_PF = (fdc_sim_PF.groupby(pd.cut(fdc_sim_PF["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_PF["p1"] =list(fdc_sim_PF.index)

fdc_sim_IF = FDC(r.q_sim_micros.FLOW_OUT_109)
fdc_sim_IF = (fdc_sim_IF.groupby(pd.cut(fdc_sim_IF["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_IF["p1"] =list(fdc_sim_IF.index)

fdc_sim_IP = FDC(r.q_sim_micros.FLOW_OUT_302)
fdc_sim_IP = (fdc_sim_IP.groupby(pd.cut(fdc_sim_IP["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_IP["p1"] =list(fdc_sim_IP.index)

fdc_sim_SC = FDC(r.q_sim_micros.FLOW_OUT_528)
fdc_sim_SC = (fdc_sim_SC.groupby(pd.cut(fdc_sim_SC["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_SC["p1"] =list(fdc_sim_SC.index)

fdc_sim_LP = FDC(r.q_sim_micros.FLOW_OUT_273)
fdc_sim_LP = (fdc_sim_LP.groupby(pd.cut(fdc_sim_LP["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_LP["p1"] =list(fdc_sim_LP.index)

fdc_sim_YF = FDC(r.q_sim_micros.FLOW_OUT_259)
fdc_sim_YF = (fdc_sim_YF.groupby(pd.cut(fdc_sim_YF["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_YF["p1"] =list(fdc_sim_YF.index)

```

Estimate PBIAS for Q5 and Q95 MICROS

```{r}

FDC_micros <- read.csv("C:/Veracruz/SWAT/SWATplusR/SWATplusR/Observed discharge/results_FDC_surface.csv")

# Estimate Q5 and Q95, compare simulated versus observed using PBIAS

pbias05_PF <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "PF"), subset(py$fdc_sim_PF$q,py$fdc_sim_PF$p1 == "0.05"))
pbias95_PF <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "PF"), subset(py$fdc_sim_PF$q,py$fdc_sim_PF$p1 == "0.95"))

pbias05_IF <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "IF"), subset(py$fdc_sim_IF$q,py$fdc_sim_IF$p1 == "0.05"))
pbias95_IF <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "IF"), subset(py$fdc_sim_IF$q,py$fdc_sim_IF$p1 == "0.95"))

pbias05_IP <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "HP"), subset(py$fdc_sim_IP$q,py$fdc_sim_IP$p1 == "0.05"))
pbias95_IP <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "HP"), subset(py$fdc_sim_IP$q,py$fdc_sim_IP$p1 == "0.95"))

pbias05_SC <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "C"), subset(py$fdc_sim_SC$q,py$fdc_sim_SC$p1 == "0.05"))
pbias95_SC <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "C"), subset(py$fdc_sim_SC$q,py$fdc_sim_SC$p1 == "0.95"))

pbias05_LP <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "LP"), subset(py$fdc_sim_LP$q,py$fdc_sim_LP$p1 == "0.05"))
pbias95_LP <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "LP"), subset(py$fdc_sim_LP$q,py$fdc_sim_LP$p1 == "0.95"))

pbias05_YF <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "YF"), subset(py$fdc_sim_YF$q,py$fdc_sim_YF$p1 == "0.05"))
pbias95_YF <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "YF"), subset(py$fdc_sim_YF$q,py$fdc_sim_YF$p1 == "0.95"))

pbias_micros <- data.frame(matrix(ncol = 3, nrow = 6))
colnames(pbias_micros) <- c("site", "pbias05", "pbias95")
pbias_micros[,1] <-c("PF", "IF", "IP","SC","LP","YF")
pbias_micros$pbias05 <- c(pbias05_PF,pbias05_IF,pbias05_IP, pbias05_SC, pbias05_LP, pbias05_YF)
pbias_micros$pbias95 <- c(pbias95_PF,pbias95_IF,pbias95_IP, pbias95_SC, pbias95_LP, pbias95_YF)
write.csv(pbias_micros, "pbias_micros.csv")

```

Convert to categorical variables FDC Gavilanes

```{python}

fdc_gav_obs = FDC(q_gav_dd.Q_m3_s)
fdc_gav_obs = (fdc_gav_obs.groupby(pd.cut(fdc_gav_obs["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_gav_obs["p1"] =list(fdc_gav_obs.index)

fdc_sim_gav = FDC(r.Gav.q_sim)
fdc_sim_gav = (fdc_sim_gav.groupby(pd.cut(fdc_sim_gav["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_gav["p1"] = list(fdc_gav_obs.index)

print(fdc_gav_obs)

```

Estimate PBIAS for Q5 and Q95 MESO

```{r}

# Estimate Q5 and Q95, compare simulated versus observed using PBIAS

pbias <- pbias(py$fdc_gav_obs$q, py$fdc_sim_gav$q)

pbias05 <- pbias(subset(py$fdc_gav_obs$q,py$fdc_gav_obs$p1 == "0.05"), subset(py$fdc_sim_gav$q,py$fdc_sim_gav$p1 == "0.05"))

pbias95 <- pbias(subset(py$fdc_gav_obs$q,py$fdc_gav_obs$p1 == "0.95"), subset(py$fdc_sim_gav$q,py$fdc_sim_gav$p1 == "0.95"))

```


```{r}

#Statistics Gavilanes

# Observed from 2015-05-02 to 2016-09-12

q_gav_c <- q_sim_gav[q_sim_gav$date %in% q_obs_gav$Date,]

nse_gav <- NSE(q_gav_c$FLOW_OUT_521,q_obs_gav$Q_m3_s)

r2_gav <- (cor(q_gav_c$FLOW_OUT_521,q_obs_gav$Q_m3_s, method="pearson"))^2

pbias <- pbias(q_gav_c$FLOW_OUT_521, q_obs_gav$Q_m3_s)

```

Make timeseries and FDC plots

```{r}

My_Theme = theme(plot.title = element_text(face = "bold", size= 16),axis.title = element_text(size= 14), 
                 axis.text = element_text(size = 18), legend.title = element_text(size=16), 
                 legend.text = element_text(size=16)) + theme_classic(base_size = 16)


  a <- ggplot() + geom_line(data=Gav, aes(Date,q_sim, colour="sim")) + 
    geom_line(data=Gav, aes(Date,q_obs, colour="obs"))+ 
    theme(legend.position="top") +labs(colour="",x=" Date", y="Discharge m^3/S") + My_Theme

  b <- ggplot() + geom_line(data=py$fdc_sim_gav, aes(p1, q, colour="sim")) + 
    geom_line(data=py$fdc_gav_obs, aes(p1, q, colour="obs")) + 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance", y="Discharge m^3/s") + My_Theme
  

  
    c <- ggplot() + geom_line(data=py$fdc_sim_PF, aes(p1,q, colour="sim PF")) + 
    geom_line(data=obs_micros, aes(P_PF,Q_PF, colour="obs PF"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  d <- ggplot() + geom_line(data=py$fdc_sim_IF, aes(p1,q, colour="sim IF")) + 
    geom_line(data=obs_micros, aes(P_IF,Q_IF, colour="obs IF"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  e <- ggplot() + geom_line(data=py$fdc_sim_IP, aes(p1,q, colour="sim IP")) + 
    geom_line(data=obs_micros, aes(P_HP,Q_HP, colour="obs IP"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  f <- ggplot() + geom_line(data=py$fdc_sim_LP, aes(p1,q, colour="sim LP")) + 
    geom_line(data=obs_micros, aes(P_LP,Q_LP, colour="obs LP"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  g <- ggplot() + geom_line(data=py$fdc_sim_SC, aes(p1,q, colour="sim SC")) + 
    geom_line(data=obs_micros, aes(P_C,Q_C, colour="obs SC"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  h <- ggplot() + geom_line(data=py$fdc_sim_YF, aes(p1,q, colour="sim YF")) + 
    geom_line(data=obs_micros, aes(P_YF,Q_YF, colour="obs YF"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  

    ggsave(file="SWAT FDC.png", plot = grid.arrange(c, d, e, f, g, h, ncol=2),scale = 1.5, width = 8, height = 8, dpi = 300)
  

```









