---
title: "R Notebook"
output: html_notebook
---

# Script 3 

Calculate statistics of fit and plots for the watersheds

```{r}
#Change the model name
q_swatt <- q_swatt
q_swatt <- q_fast$simulation$q_out%>%
  select(date,run_0861)

# left join to use only observed data in gavilanes m3/s

gav <- q_obs_gav %>%
  select(Date, Q_m3_s) %>%
  rename(q_obs = Q_m3_s)%>%
  left_join(., q_swatt, by = c("Date"="date")) %>%
  rename(q_sim = run_0861)%>%
  select(Date,q_obs,q_sim)

#Extract simulated Q microwatersheds

#q_sim_micros <- q_swatt[4:9]%>%
#  as.data.frame(t(t(q_sim_micros)*((86400/micros$Area_m2)*1000))) # (60*60*24/A)*1000 convert to mm day-1

```

Statistics gavilanes
```{r}

#Statistics Gavilanes

print(paste('NSE = ', NSE(gav$q_sim, gav$q_obs)))

print(paste('R^2 =', (cor(gav$q_sim,gav$q_obs, method="pearson"))^2))

print(paste('Pbias = ',pbias(gav$q_sim, gav$q_obs))) 

```

#Use python to estimate FDC and equal number of bins.


```{python}

#Declare the FDC function

def FDC (q):
    
    """ This function computes the FDC q is the dataframe column with Q values"""
    
    data = np.asarray(q[q.notnull()])
    
    data = -np.sort(-data,)
    
    name = pd.DataFrame(list(data))
    
    name["p"] = (name.index + 1)/(len(name) + 1)

    name.columns = ["q", "p"]
    
    return name

#Calculates FDC for obs gavilanes
fdc_gav_obs = FDC(r.gav.q_obs)

#Calculate 99 bins 0.1 - 0.99 obs gavilanes
fdc_gav_obs = (fdc_gav_obs.groupby(pd.cut(fdc_gav_obs["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1] 
fdc_gav_obs["p1"] =list(fdc_gav_obs.index)

#Calculates FDC for sim gavilanes = observed
fdc_sim_gav = FDC(r.gav.q_sim)

#Calculates bins for sim gavilanes
fdc_sim_gav = (fdc_sim_gav.groupby(pd.cut(fdc_sim_gav["p"], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
fdc_sim_gav["p1"] = list(fdc_gav_obs.index)

```

# Compute FDC for simulated

```{python}

#Create empty dataframe
fdc_sim = pd.DataFrame()

for col in r.q_swatt.columns[1:]:
  #Apply fdc function
  fdc = FDC(r.q_swatt[col])
  #Calculate 99 bins [0.1 - 0.99]
  fdc = (fdc.groupby(pd.cut(fdc['p'], bins = np.linspace(-0.005, 1.005, 102), labels= np.linspace(0, 1, 101))).mean())[1:-1]
  # Appends a new column and names it
  fdc_sim[col] = fdc['q']  
#Adds the probability
fdc_sim['p'] = fdc['p']

print(fdc_sim)
```

Estimate PBIAS for Q5 and Q95 in Gavilanes

```{r}

# Estimate Q5 and Q95, compare simulated versus observed using PBIAS

print(paste("pbias = ", pbias(py$fdc_gav_obs$q, py$fdc_sim_gav$q)))
print(paste("pbias_05 = ", pbias(subset(py$fdc_gav_obs$q,py$fdc_gav_obs$p1 == "0.05"), subset(py$fdc_sim_gav$q,py$fdc_sim_gav$p1 == "0.05"))))
print(paste("pbias_95 = ", pbias(subset(py$fdc_gav_obs$q,py$fdc_gav_obs$p1 == "0.95"), subset(py$fdc_sim_gav$q,py$fdc_sim_gav$p1 == "0.95"))))

```

Make timeseries and FDC plots

```{r}

My_Theme = theme(plot.title = element_text(face = "bold", size= 16),axis.title = element_text(size= 14), 
                 axis.text = element_text(size = 18), legend.title = element_text(size=16), 
                 legend.text = element_text(size=16)) + theme_classic(base_size = 16)

ggplot() + geom_line(data=gav, aes(Date,q_sim, colour="sim")) + 
    geom_line(data=gav, aes(Date,q_obs, colour="obs"))+ 
    theme(legend.position="top") +labs(colour="",x=" Date", y="Discharge m^3/S") + My_Theme

ggplot() + geom_line(data=py$fdc_sim_gav, aes(p1, q, colour="sim")) + 
    geom_line(data=py$fdc_gav_obs, aes(p1, q, colour="obs")) + 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance", y="Discharge m^3/s") + My_Theme
  
```

#Plot FDC obs vs sim microwatersheds
GA = FLOW_OUT_521
PI = FLOW_OUT_326

PF = FLOW_OUT_355
IF = FLOW_OUT_109
IP = FLOW_OUT_302
LP = FLOW_OUT_273
SC = FLOW_OUT_528
YF = FLOW_OUT_259

```{r}

fdc_sim = py$fdc_sim

p <- list() # Empty list of plots

My_Theme = theme(plot.title = element_text(face = "bold", size= 16),axis.title = element_text(size= 14), 
                 axis.text = element_text(size = 18), legend.title = element_text(size=16), 
                 legend.text = element_text(size=16)) + theme_classic(base_size = 16)

  p[[1]] <- ggplot() + geom_line(data=fdc_sim, aes(p,FLOW_OUT_355, colour="sim PF")) + 
    geom_line(data=obs_micros, aes(P_PF,Q_PF, colour="obs PF"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  p[[2]] <- ggplot() + geom_line(data=fdc_sim, aes(p,FLOW_OUT_109, colour="sim IF")) + 
    geom_line(data=obs_micros, aes(P_IF,Q_IF, colour="obs IF"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  p[[3]] <- ggplot() + geom_line(data=fdc_sim, aes(p,FLOW_OUT_302, colour="sim IP")) + 
    geom_line(data=obs_micros, aes(P_HP,Q_HP, colour="obs IP"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  p[[4]] <- ggplot() + geom_line(data=fdc_sim, aes(p,FLOW_OUT_273, colour="sim LP")) + 
    geom_line(data=obs_micros, aes(P_LP,Q_LP, colour="obs LP"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  p[[5]] <- ggplot() + geom_line(data=fdc_sim, aes(p,FLOW_OUT_528, colour="sim SC")) + 
    geom_line(data=obs_micros, aes(P_C,Q_C, colour="obs SC"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme
  
  p[[6]] <- ggplot() + geom_line(data=fdc_sim, aes(p,FLOW_OUT_259, colour="sim YF")) + 
    geom_line(data=obs_micros, aes(P_YF,Q_YF, colour="obs YF"))+ 
    theme(legend.position="top") + scale_y_continuous(trans="log10") +labs(colour="",x=" Prob. of exceedance",
       y="Discharge mm/day") + My_Theme

    ggsave(file="SWAT FDC.png", plot = grid.arrange(p[[1]], p[[2]], p[[3]], p[[4]], p[[5]], p[[6]], ncol=2),scale = 1.5, width = 8, height = 8, dpi = 300)
  
```

Estimate PBIAS for Q5 and Q95 microwatersheds

```{r}



# Estimate Q5 and Q95, compare simulated versus observed using PBIAS

pbias05_PF <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "PF"), subset(py$fdc_sim_PF$q,py$fdc_sim_PF$p1 == "0.05"))
pbias95_PF <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "PF"), subset(py$fdc_sim_PF$q,py$fdc_sim_PF$p1 == "0.95"))

pbias05_IF <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "IF"), subset(py$fdc_sim_IF$q,py$fdc_sim_IF$p1 == "0.05"))
pbias95_IF <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "IF"), subset(py$fdc_sim_IF$q,py$fdc_sim_IF$p1 == "0.95"))

pbias05_IP <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "HP"), subset(py$fdc_sim_IP$q,py$fdc_sim_IP$p1 == "0.05"))
pbias95_IP <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "HP"), subset(py$fdc_sim_IP$q,py$fdc_sim_IP$p1 == "0.95"))

pbias05_SC <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "C"), subset(py$fdc_sim_SC$q,py$fdc_sim_SC$p1 == "0.05"))
pbias95_SC <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "C"), subset(py$fdc_sim_SC$q,py$fdc_sim_SC$p1 == "0.95"))

pbias05_LP <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "LP"), subset(py$fdc_sim_LP$q,py$fdc_sim_LP$p1 == "0.05"))
pbias95_LP <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "LP"), subset(py$fdc_sim_LP$q,py$fdc_sim_LP$p1 == "0.95"))

pbias05_YF <- pbias(subset(FDC_micros$X0.05,FDC_micros$names == "YF"), subset(py$fdc_sim_YF$q,py$fdc_sim_YF$p1 == "0.05"))
pbias95_YF <- pbias(subset(FDC_micros$X0.95,FDC_micros$names == "YF"), subset(py$fdc_sim_YF$q,py$fdc_sim_YF$p1 == "0.95"))

pbias_micros <- data.frame(matrix(ncol = 3, nrow = 6))

colnames(pbias_micros) <- c("site", "pbias05", "pbias95")

pbias_micros[,1] <-c("PF", "IF", "IP","SC","LP","YF")

pbias_micros$pbias05 <- c(pbias05_PF,pbias05_IF,pbias05_IP, pbias05_SC, pbias05_LP, pbias05_YF)
pbias_micros$pbias95 <- c(pbias95_PF,pbias95_IF,pbias95_IP, pbias95_SC, pbias95_LP, pbias95_YF)
write.csv(pbias_micros, "pbias_micros.csv")

```





