---
title: "Parameter sensitivity analysis"
output: html_notebook
---

Loading R packages

```{r}

library(SWATplusR)
library(sensitivity)
library(fast)
library(hydroGOF)
library(dplyr)
library(forcats)
library(tidyr)
library(ggplot2)
library(lhs)
library(purrr)
library(lubridate)


```

Loading model

```{r}
# The path where the SWAT project is written

path_2012 <- "C:/Veracruz/SWAT/github-rswat-ver/swat_models/sim_swat_t"

# Daily observed discharge gavilanes outlet (2015-05-02 to 2016-09-12)
q_obs <- q_obs_gav 

```

#Influential pars in the hydrology of tropical areas.

Manual calibration of LAI growth: 
r__SOL_ALB().sol                     -0.3   0.3
r__BLAI{1,2,40,6,12,94}.plant.dat    -0.9   0.9
r__CANMX.hru                         -0.4   0.4

Calibration based on observed data SD/mean:
r__SOL_AWC().sol  -0.35  0.35
r__SOL_K().sol    -0.8   0.8
r__SOL_Z().sol    -0.3   0.3
r__CN2.mgt        -0.25  0.25

Arbitrary calibration:
v__ALPHA_BF.gw    0        1
v__GW_DELAY.gw    0        650
v__GW_REVAP.gw    0.02     0.2
v__GWQMN.gw       0        2000
v__RCHRG_DP.gw    0        1
v__REVAPMN.gw     0        500
v__CH_K2.rte	    5        130
v__CH_N2.rte	    0        0.3
v__EPCO.hru       0        1
v__ESCO.hru       0        1
r__HRU_SLP.hru    -0.2     0.2
r__SLSUBBSN.hru   -0.3     0.3
v__SURLAG.bsn     0        10

# Type of change
r = ‘relchg’, multiply
v = “absval”, replace
a = “abschg”, add 
    'pctchg', 

Define the parameter names in SWAT2012, these are equal to SWATCUP

```{r}
par_names <- c("SOL_AWC.sol|change = relchg",
               "SOL_K.sol|change = relchg",
               "SOL_Z.sol|change = relchg",
               "CN2.mgt|change = relchg",
               "ALPHA_BF.gw|change = absval",
               "GW_DELAY.gw|change = absval",
               "GW_REVAP.gw|change = absval",
               "GWQMN.gw|change = absval",
               "RCHRG_DP.gw|change = absval",
               "REVAPMN.gw|change = absval",
               "CH_K2.rte|change = absval",
               "CH_N2.rte|change = absval",
               "EPCO.hru|change = absval",
               "ESCO.hru|change = absval",
               "HRU_SLP.hru|change = relchg",
               "SLSUBBSN.hru|change = relchg",
               "SURLAG.bsn|change = absval"
               )
```


#Sensitivity analysis with FAST

The Fourier Amplitude Sensitivity Test (FAST) is a method to perform GSA with few model evaluations
## Parameter sampling
```{r}
#Parameter sampling with the FAST method requires a specific parameter sampling desing, that is avaialble with the fast function fast_parameters()

par_fast <- fast_parameters(
  minimum = c(-0.35, -0.8, -0.3, -0.25, 0, 0, 0.02, 0, 0, 0, 5, 0, 0, 0, -0.2, -0.3, 0),
  maximum = c(0.35, 0.8, 0.3, 0.25, 1, 650, 0.2, 2000, 1, 500, 130, 0.3, 1, 1, 0.2, 0.3, 10),
  names = par_names) %>%
  as_tibble()

```

## Model simulation and evaluation 


To perform a FAST analysis for 17 parameters 1367 model evaluations are required (16 hrs)
```{r}
#Model simulation and evaluation, uses 2 cpus with 2 Threads each, total of 4 threads

q_fast <- run_swat2012(project_path = path_2012,
            output = list(q_out = define_output(file = "rch",
                                  variable = "FLOW_OUT",
                                  unit = 15)), # gavilanes = 15, pixquiac = 14
            parameter = par_fast,
            start_date = "2014-01-01",
            end_date = "2017-12-31",
            years_skip = 1,
            n_thread = 4)
```

The model runs are evaluated using the NSE criterion for daily discharge from 2015-05-02 to 2017-04-30

```{r}

#Find the date in q_sim which are present in Date column of q_obs

q_fast_c <- q_fast$simulation$q_out[q_fast$simulation$q_out$date %in% q_obs$Date,]

#Model evaluation

nse_fast <- q_fast_c %>%
  select(-date) %>%
  map_dbl(., ~NSE(.x, q_obs$Q_m3_s))

#Nash sutclife
nse_fast <- q_fast$simulation$q_out%>%
  subset(date %in% q_obs$Date,)%>% # Subset TRUE when date from sim is dat obs 
  select(-date)%>% # Apply for each simulation reusing date
  map_dbl(., ~NSE(., q_obs$Q_m3_s)) # Apply NSE function using q_sim, q_obs

#Coefficient of determination
r2_fast <- q_fast$simulation$q_out%>%
  subset(date %in% q_obs$Date,)%>% # Subset TRUE when date from sim is dat obs 
  select(-date)%>% # Apply for 
  map_dbl(., ~cor(., q_obs$Q_m3_s, method="pearson")^2) # Apply NSE function using q_sim, q_obs


#Statistics 

sens_fast <- sensitivity(nse_fast, 17) # These are the number of parameters


```

#Visualization of the FAST sensitivities

We convert the parameter names to factors and sort them according to their sensitivity results using the functionality of the forcats package (Wickham, 2019). We plot the parameter ranking in a barplot using ggplot2 (Wickham, 2016).

```{r}

#higher senstitivities change depending on the statistics of fit

result_fast <- tibble(parameter = q_fast$parameter$definition$par_name,
                      fast      = sens_fast) %>%
  mutate(parameter = factor(parameter) %>% fct_reorder(., fast))


ggplot(data = result_fast) +
  geom_bar(aes(x = parameter, y = fast), stat = "identity") +
  xlab("Parameter") +
  ylab("Sensitivity") +
  coord_flip() +
  theme_bw()+
  theme(text = element_text(size = 14))

```


