---
title: "R Notebook"
output: html_notebook
---

#Loading R packages

```{r}
library(SWATplusR)
library(sensitivity)
library(fast)
library(hydroGOF)
library(dplyr)
library(forcats)
library(tidyr)
library(ggplot2)
library(lhs)
library(purrr)
library(lubridate)
library(magrittr)
library(reshape2)

```

#Loading model

```{r}
# The path where the SWAT project is written
path_2012 <- "C:/Veracruz/SWAT/github-rswat-ver/swat_models/swat_t_canmx"

```


# Type of change
r = ‘relchg’, multiply
v = “absval”, replace
a = “abschg”, add 

#Latin Hypercube sampling (15 pars) previously selected

```{r}
par_bound <- tibble("SOL_AWC.sol|change = relchg" = c(-0.35, 0.35), #Data
               "SOL_K.sol|change = relchg" = c(-0.8, 0.8), #Data
               "ALPHA_BF.gw|change = absval" = c (0, 0.3), #Data
               "RCHRG_DP.gw|change = absval" = c(0, 1),
               "CN2.mgt|change = abschg" = c(-15, 15),
               "ALPHA_BNK.rte|change = absval" = c(0, 1), # Channels
               "CH_N2.rte|change = absval" = c(0, 0.3),
               "CH_K2.rte|change = absval" = c(5, 130),
               "LAT_TTIME.hru|change = absval" = c(0, 180),
               "SLSOIL.hru|change = absval" = c(0, 150),
               "ESCO.hru|change = absval" = c(0, 1),
               "DEP_IMP.hru|change = absval" = c(0, 6000),
               "HRU_SLP.hru|change = relchg"= c(-0.2, 0.2),
               "EPCO.hru|change = absval" = c(0, 1),
               "GW_DELAY.gw|change = absval"= c(0, 500)
               )

n_sample <- 5000
n_par <- ncol(par_bound)

#Latin hypercube sampling
par_pwn <- randomLHS(n = n_sample, k = n_par) %>%
  as_tibble(., .name_repair = "minimal") %>%
  map2_df(., par_bound, ~ (.x * (.y[2] - .y[1]) + .y[1])) %>%
  set_names(names(par_bound))


sim_pwn <- run_swat2012(project_path = path_2012,
            output = list(q_out = define_output(file = "rch",
                                  variable = "FLOW_OUT",
                                  unit = c(6,15))), # gavilanes = 15, pixquiac = 6
            parameter = par_pwn,
            start_date = "2014-01-01",
            end_date = "2017-12-31",
            years_skip = 1,
            n_thread = 2)

```


#Latin Hypercube sampling (16 pars) previously selected

```{r}
par_bound <- tibble("SOL_AWC.sol|change = relchg" = c(-0.35, 0.35), #Data
               "SOL_K.sol|change = relchg" = c(-0.8, 0.8), #Data
               "ALPHA_BF.gw|change = absval" = c (0, 0.3), #Data
               "RCHRG_DP.gw|change = absval" = c(0, 1),
               "CN2.mgt|change = abschg" = c(-15, 15),
               "ALPHA_BNK.rte|change = absval" = c(0, 1), # Channels
               "CH_N2.rte|change = absval" = c(0, 0.3),
               "CH_K2.rte|change = absval" = c(5, 130),
               "LAT_TTIME.hru|change = absval" = c(0, 180),
               "SLSOIL.hru|change = absval" = c(0, 150),
               "ESCO.hru|change = absval" = c(0, 1),
               "DEP_IMP.hru|change = absval" = c(0, 6000),
               "HRU_SLP.hru|change = relchg"= c(-0.2, 0.2),
               "EPCO.hru|change = absval" = c(0, 1),
               "GW_DELAY.gw|change = absval"= c(0, 500),
               "GW_SPYLD.gw|change = absval" = c(0, 0.4)
               )

n_sample <- 5000
n_par <- ncol(par_bound)

#Latin hypercube sampling
par_pwn2 <- randomLHS(n = n_sample, k = n_par) %>%
  as_tibble(., .name_repair = "minimal") %>%
  map2_df(., par_bound, ~ (.x * (.y[2] - .y[1]) + .y[1])) %>%
  set_names(names(par_bound))


sim_pwn2 <- run_swat2012(project_path = path_2012,
            output = list(q_out = define_output(file = "rch",
                                  variable = "FLOW_OUT",
                                  unit = c(6,15))), # gavilanes = 15, pixquiac = 6
            parameter = par_pwn2,
            start_date = "2014-01-01",
            end_date = "2017-12-31",
            years_skip = 1,
            n_thread = 4)


#Here we store the first sim in as 1
sim_pwn1 <- sim_pwn
par_pwn1 <-par_pwn


# Here we choose the sim to work with

sim_pwn<- sim_pwn2
par_pwn <-par_pwn2

```

#The model runs are evaluated using the R2, NSE, and KGE criterion in Gavilanes

```{r}
#Gavilanes

#Adding results to Gavilanes
gav$sim_pwn <- sim_pwn$simulation$q_out_15[sim_pwn$simulation$q_out_15$date %in% gav$obs$Date,]

#Calculate max and min
gav$obs$q5 <- apply(gav$sim_pwn[2:ncol(gav$sim_pwn)],1 , function(x) min(as.numeric(x)))

gav$obs$q95 <- apply(gav$sim_pwn[2:ncol(gav$sim_pwn)],1 , function(x) max(as.numeric(x)))


#Nash–Sutcliffe efficiency 
gav$nse <- gav$sim_pwn %>%
  select(-date) %>%
  map_dbl(., ~NSE(.x, gav$obs$Q_m3_s))

#Coefficient of determination
gav$r2 <- gav$sim_pwn%>%
  select(-date)%>%
  map_dbl(., ~cor(., gav$obs$Q_m3_s, method="pearson")^2)

# Kling-Gupta efficiency criterion (KGE)
gav$kge <- gav$sim_pwn%>%
  select(-date)%>%
  map_dbl(., ~KGE(., gav$obs$Q_m3_s))


#Create the for gav

gav$fdc_sim <- gav$sim_pwn%>%
  select(-date)%>%
  lapply(., sort, decreasing = T)%>%
  lapply(FUN=unlist)%>%
  as_data_frame()

gav$fdc_sim$p <- seq(0,1,length.out= length(gav$fdc_sim[[1]]))

  
#Calculate RSR for different signatures

#Very high flow < Q5
gav$rsr_Q05 <- gav$fdc_sim[gav$fdc_sim$p<0.05,]%>% # Subset matrix with a prob. of exceedence
  map_dbl(., ~rsr(.,gav$fdc$Q_m3_s[gav$fdc$p<0.05]))# Subset obs with a prob. of exceedence

# High flows Q5-Q20
gav$rsr_Q5_20 <- gav$fdc_sim[gav$fdc_sim$p>0.05 & gav$fdc_sim$p<0.20,]%>% # Subset matrix with a prob. of exceedence
  map_dbl(., ~rsr(.,gav$fdc$Q_m3_s[gav$fdc$p>0.05 & gav$fdc$p<0.20]))# Subset obs with a prob. of exceedence

# Mid flow Q20-Q70
gav$rsr_Q20_70 <- gav$fdc_sim[gav$fdc_sim$p>0.20 & gav$fdc_sim$p<0.70,]%>% # Subset matrix with a prob. of exceedence
  map_dbl(., ~rsr(.,gav$fdc$Q_m3_s[gav$fdc$p>0.20 & gav$fdc$p<0.70]))# Subset obs with a prob. of exceedence

#Low flow Q70 -Q95
gav$rsr_Q70_95 <- gav$fdc_sim[gav$fdc_sim$p>0.70 & gav$fdc_sim$p<0.95,]%>% # Subset matrix with a prob. of exceedence
  map_dbl(., ~rsr(.,gav$fdc$Q_m3_s[gav$fdc$p>0.70 & gav$fdc$p<0.95]))# Subset obs with a prob. of exceedence

# Very low flow > Q95
gav$rsr_Q95 <- gav$fdc_sim[gav$fdc_sim$p>0.95,]%>% # Subset matrix with a prob. of exceedence
  map_dbl(., ~rsr(.,gav$fdc$Q_m3_s[gav$fdc$p>0.95]))# Subset obs with a prob. of exceedence


```

#Select the best parameter sets according to KGE and 5 signature metrics

```{r}
bestpar <-  list()

#Selecting the best parameter sets
bestpar$best25 <- sim_pwn$parameter$values[c(order(gav$nse, decreasing = T)[1:20]),]%>%
  mutate(sim = order(gav$nse, decreasing=T)[1:20])

#Selecting the best parameter sets
bestpar$best <- sim_pwn$parameter$values[c(
  Reduce(intersect, list(
  order(gav$rsr_Q05, decreasing=F)[1:up], #RSR min values are better
  order(gav$rsr_Q5_20, decreasing=F)[1:up],
  order(gav$rsr_Q20_70, decreasing=F)[1:up],
  order(gav$rsr_Q70_95, decreasing=F)[1:up],
  order(gav$rsr_Q95, decreasing=F)[1:up],
  order(gav$kge, decreasing=T)[1:up] #KGE larger values are better
))
),]

#Correlation between parameters
library(corrplot)
corrplot(cor(bestpar$best25), type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

```

#Plot the best sims in gavilanes

```{r}

#Plot the best sims using KGE

bestpar$bestsims <- data.frame(gav$sim_pwn[c(0,order(gav$rsr_Q95, decreasing=F)[1:30])+1])%>%# Including date 1
  melt(.,  id.vars = 'date', variable.name = 'series')

ggplot(bestpar$bestsims, aes(date,value)) + geom_line(aes(colour = "series"))+
  geom_line(data=gav$sim_pwn, aes(date, run_1233, colour ="best sim"))+
  geom_line(data=gav$obs, aes(Date, Q_m3_s))


#fdc  
bestpar$simsgav <- data.frame(gav$sim_pwn[c(order(gav$rsr_Q95, decreasing=F)[1:30])+1])%>%
  lapply(., sort, decreasing=T)%>%
  data.frame(.)%>%
  mutate(p = seq(0,1, length.out = nrow(.)))%>%
  melt(.,  id.vars = 'p', variable.name = 'series') #To long dataframe

ggplot(bestpar$simsgav, aes(p,value)) + geom_line(aes(colour = "series")) + 
  geom_line(data=gav$fdc, aes(p, Q_m3_s))+
  scale_y_continuous(trans="log2")


```

#Lets intersect the best 25 quantile of the simulations considering RSRQ95 and KGE

```{r}

up <- 2000

print(
Reduce(intersect, list(
  order(gav$rsr_Q05, decreasing=F)[1:up], #RSR min values are better
  order(gav$rsr_Q5_20, decreasing=F)[1:up],
  order(gav$rsr_Q20_70, decreasing=F)[1:up],
  order(gav$rsr_Q70_95, decreasing=F)[1:up],
  order(gav$rsr_Q95, decreasing=F)[1:up],
  order(gav$kge, decreasing=T)[1:up] #KGE larger values are better
))
)

#Timeseries

bestpar$bestsims <- data.frame(gav$sim_pwn[c(0,
                                             Reduce(intersect, list(
                                                 order(gav$rsr_Q05, decreasing=F)[1:up], #Very high flows
                                                 order(gav$rsr_Q5_20, decreasing=F)[1:up],
                                                 order(gav$rsr_Q20_70, decreasing=F)[1:up],
                                                 order(gav$rsr_Q70_95, decreasing=F)[1:up],
                                                 order(gav$rsr_Q95, decreasing=F)[1:up], #Very low flows
                                                 order(gav$kge, decreasing=T)[1:up] #KGE larger values are better
                                                 ))
                                             )+1])%>%# Including date 1
  melt(.,  id.vars = 'date', variable.name = 'series')


ggplot(bestpar$bestsims, aes(date,value)) + geom_line(aes(colour = "series"))+
  geom_line(data=gav$sim_pwn, aes(date, run_1233, colour ="best sim"))+
  geom_line(data=gav$obs, aes(Date, Q_m3_s))


#fdc  
bestpar$simsgav <- data.frame(gav$sim_pwn[c(
  Reduce(intersect, list(
  order(gav$rsr_Q05, decreasing=F)[1:up], #Very high flows
  order(gav$rsr_Q5_20, decreasing=F)[1:up],
  order(gav$rsr_Q20_70, decreasing=F)[1:up],
  order(gav$rsr_Q70_95, decreasing=F)[1:up],
  order(gav$rsr_Q95, decreasing=F)[1:up], #Very low flows
  order(gav$kge, decreasing=T)[1:up] #KGE larger values are better
  ))
  )+1])%>%
  lapply(., sort, decreasing=T)%>%
  data.frame(.)%>%
  mutate(p = seq(0,1, length.out = nrow(.)))%>%
  melt(.,  id.vars = 'p', variable.name = 'series') #To long dataframe


ggplot(bestpar$simsgav, aes(p,value)) + geom_line(aes(colour = series)) + 
  geom_line(data=gav$fdc, aes(p, Q_m3_s))+
  scale_y_continuous(trans="log2")


print(c("R^2 = ", (cor(gav$sim_pwn$run_1233, gav$obs$Q_m3_s))^2,
          "NSE = ", NSE(gav$sim_pwn$run_1233, gav$obs$Q_m3_s),
          "KGE = ", KGE(gav$sim_pwn$run_1233, gav$obs$Q_m3_s),
          "PBIAS = ", pbias(gav$sim_pwn$run_1233, gav$obs$Q_m3_s)))

```

